\documentclass[12pt,2up]{article}
%{{{1
\usepackage{mathpazo}
\usepackage{fullpage}
\special{papersize=8.5in,11in}
\usepackage[LabelsAligned]{currvita}
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\setlength{\parskip}{0.8mm}
\usepackage{eurosym} 
\usepackage[latin9]{inputenc}
\pagecolor{white}
%\usepackage{srcltx}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\setlength{\cvlabelsep}{2mm}
\setlength{\cvlabelwidth}{13mm}
%}}}1
\begin{cv}{} 
\begin{center}
CURRICULUM VITAE\\
\vspace{.25in}
\textbf{\textsc{Daniel Arribas-Bel}
}
\end{center}
%{{{1
\begin{center}
\begin{tabular}{c}
    Department of Geography and Planning \\
    University of Liverpool \\
    Roxby Building \\
    74 Bedford St S \\
    Liverpool \\
    L69 7ZT \\
    United Kingdom \\
    \\
    {\small D.Arribas-Bel@liverpool.ac.uk} \hspace{0.5cm}
	{\small https://darribas.org}
\end{tabular}
\end{center}
  %}}}1
 \begin{cvlist}{Education}
 %{{{1

\item[2010] PhD Economics, Universidad de Zaragoza (Spain).
    \begin{itemize}
        \item[] \textit{Essays on the Distribution and Spatial Structure of
            Cities.}
        \item[\begin{small}Supervisor:\end{small}] \begin{small}Fernando
                Sanz-Gracia.\end{small} 
        \item[\begin{small}Committee:\end{small}] \begin{small}Prof. Michael J. Batty (chair), Prof. Sergio J. Rey, Prof. Enrique Lopez Bazo, Dr. Rafael Boix Domenech.\end{small} 
    \end{itemize}
\item[2008] MSc. Economics, Universidad de Zaragoza (Spain).
    \begin{itemize}
        \item[] \textit{Kangaroos, Cities and Space: a First Approach to the
            Australian Urban System}.
    \end{itemize}
\item[2006] BS. Economics, Universidad de Zaragoza (Spain).
  \end{cvlist}

  %}}}1

   \begin{cvlist}{Current Academic Appointments}
 %{{{1

 \item[2022-] Professor in Geographic Data Science, Department of Geography and
     Planning, University of Liverpool.
 \item[2025-] Co-Director. Imago Smart Data Research UK Data Service for
         Imagery.

  \end{cvlist}

   \begin{cvlist}{Honorary Appointments}

 \item[2022-] Affiliate, Center for Open Geographical Science, San Diego State
         University.

 \item[2016-] Fellow, Center for Spatial Data Science, University of Chicago.

 \item[2006-] Researcher, ADETRE Research Group, Universidad de Zaragoza.

 \item[2020-2022] Honorary Senior Lecturer, Department of Computer Science,
     University of Liverpool.

 \item[2018-2022] Affiliate, Center for Geospatial Sciences, University of
     California Riverside.

 \item[2017-2019] Member, Smart Cities UB Chair, Universitat de Barcelona.

  \end{cvlist}

  %}}}1

   \begin{cvlist}{Editorial Appointments}
   \item[2019-] Co-editor, \textit{Environment and Planning B -
       Urban Analytics and City Science}
   \item[2025-] Editorial Board, \textit{Annals of the American Association of
           Geographers}
   \item[2021-] Editorial Board, \textit{Journal of Geographical Systems}
   \item[2019-] Editorial Board, \textit{Spatial Economic
       Analysis}
   \item[2017-] Editorial Board, \textit{Geographical Analysis}.
   \item[2020-2024] Associate Editor, \textit{Journal of the Royal Statistical Society
       Series A - Statistics in Society}
   \item[2016-2022] Editorial Board, \textit{Transactions in GIS}.
   \item[2015-2018] Book Reviews Editor, \textit{Environment and Planning B -
       Urban Analytics and City Science}.
  \end{cvlist}
  %}}}1

\begin{cvlist}{Other Appointments}
\item[2021-] Steering committee, workstream coordinator Urban Analytics. The OECD
    Laboratory for Geospatial Analysis. OECD.
\item[2016-2022] Programme Director, MSc in Geographic Data Science, University
of Liverpool.
\item[2017-2022] Chair, Quantitative Methods Research Group, Royal
    Geographical Society.
\end{cvlist}
  %}}}1

   \begin{cvlist}{Prior Academic Appointments}

 %{{{1

 \item[2021-2025] Deputy Programme Director, Urban Analytics, The Alan Turing Institute.
 \item[2020-2023] ESRC Fellow, The Alan Turing Institute.
 \item[2018-2022] Senior Lecturer in Geographic Data Science, Department of Geography and
     Planning, University of Liverpool.
  \item[2015-2018] Lecturer in Geographic Data Science, Department of Geography and
     Planning, University of Liverpool.
\item[2012-2016] Research Associate, GeoDa Center for Geospatial Analysis
    and Computation, Arizona State University.

 \item[2014-2015] Lecturer in Human Geography, School of Geography, Earth and
     Environmental Sciences, University of Birmingham (UK).

 \item[2012-2014] Postdoctoral researcher, Department of Spatial Economics, Vrije Universiteit.

 \item[2011-2012] Postdoctoral Research Associate, GeoDa Center for Geospatial Analysis
    and Computation, Arizona State University.

\item[2006-2010] PhD Student, Department of Economic Analysis, Universidad de
    Zaragoza.

  \end{cvlist}

  %}}}1
\begin{cvlist}{Honors and Awards}
%{{{1 

\item[2026] \emph{Media Achievement Award} for the GLaD podcast. American Association of
        Geographers. Joint with Rachel Frankling and Levi Wolf.
\item[2024] \emph{Taylor \& Francis Award} for ``excellence in the practice and
        promotion of teaching in higher education``. Royal Geographical Society.
\item[2021] \emph{``Keeping the conversation going`` - The use of Teams
        to sustain engagement in Geographic Data Science learning}. Faculty
        Learning, Teaching and Student Experience Award Winner. Faculty of
        Science and Engineering. University of Liverpool.
\item[2020] \emph{Spatial Data Scientist of the Year} (inaugural). Spatial Data Science
        Conference (Online). CARTO.
\item[2006] \emph{Premio extraordinario de licenciatura} (Best student of the
    year in economics at the University of Zaragoza).

 %\item[1999-00] Faculty Fellow. Center on Computational Science and
 % Engineering. San Diego State University.
  \end{cvlist}

 \begin{cvlist}{Research Income}

\item[\textbf{Awards}]
%{{{1
\item[2024] \emph{Economic and Social Research Council, UK Research and
        Innovation} - ``The SDR UK Imagery
        Data Service for Sustainability, Prosperity and Wellbeing (Imago)''.
        Smart Data Research UK Data Services. PI. 2024/29. \pounds6,788,641
    %https://www.ukri.org/opportunity/smart-data-research-uk-data-services/
\item[] \emph{The Royal Society} - ``Learning from UK-France cross border railway transportation:
        border effect modelling and operational modes for the China-Laos Railway''.
        International Exchanges. CoI. \pounds12,000.
\item[] \emph{European Space Agency} - ``EuroFab: European Urban Fabric
        Classification Using Artificial Intelligence''.
        Tender. CoI. \euro250,000.
\item[] \emph{European Space Agency} - ``EO Informed Agent Based Models
        for Digital Twins Applications''. Tender. CoI. \euro399,739.
\item[2023] \emph{Geospatial Commission} - ``National Land Data Programme
        Turing Demonstrator Extension''. 
        Grant funding agreement with the Geospatial Commission (Department for
        Science, Innovation and Technology). PI. \pounds99,955.
\item[2022] \emph{Geospatial Commission} -
        ``Using scenario-based land use modelling to identify the impacts from
        policy demands on land use change in a large conurbation''.
        Grant funding agreement for the National Land Data Programme - Land
        Use Demonstrator. PI. 2022/23. \pounds182,329
\item[] \emph{The Alan Turing Institute} -
        ``The Science of Cities and Regions''. Out of budget process. Co-I.
        2022/25. \pounds2,996,046
\item[] \emph{Economic and Social Research Council (ESRC)} -
``Supporting Post Pandemic Recovery and Resilience through New Forms of Data''.
ESRC AHRC UK South Korea SSH Connections Grants. CoI. 2022/23. \pounds138,893.36.
\item[] \emph{Fundaci\'{o}n La Caixa} -
    ``Building and shaping cities for a healthy and prosperous future''.
    Social Research Grants. CoI. 2022/23. 100,000\euro.
\item[] \emph{Engineering and Physical Sciences Research Council (EPSRC)}
        - ``ITINERANT: InequaliTies IN Experiencing uRbAn fuNcTion. Cuebiq
        data subscription''. CoI. 2022. \pounds14,000
\item[2021] \emph{Engineering and Physical Sciences Research Council
    (EPSRC)/The Alan Turing Institute}
    - ``InequaliTies IN Experiencing uRbAn fuNcTion (ITINERANT)''. PI.
    2021/22. \pounds96,624
\item[] \emph{Natural Environment Research Council (NERC)} - ``Nitrogen Fixation in the 
    Arctic Ocean''. Standard grant, \texttt{NE/T001240/1}. CoI. 2021/23. \pounds 733,137
\item[2020] \emph{Economic and Social Research Council (ESRC)} - ``Learning an
    urban grammar from satellite data through AI''. Joint ESRC/The Alan Turing Institute
    Fellowship, \texttt{ES/T005238/1}.
    PI. 2020/23. \pounds426,224
\item[] \emph{Maritime Research and Innovation UK} (MarRI-UK) - ``Assuring
    safe port navigation by applying machine learning (ML) to wave data for
    automated monitoring of changes in nearshore bathymetry''. CoI. 2020/21.
    \pounds169,232
\item[2019] \emph{University of Liverpool Industrial Strategy Fund - ``Envisaging Liverpool's Future Digital City Region and Smart
    Governance''}. Together with Prof. Alex Singleton (PI) and Prof. Mark
    Boyle (CoI). CoI. \pounds23,000
\item[] \emph{Kings College London Faculty Education Fund - ``Conjuring:
    Self-Contained Jupyter Hub for Teaching''}. Together with Dr. Jon Reades
    (PI) and Dr. Steffen Zschaler (CoI). CoI. \pounds4,975
\item[2018] \emph{ODA Research Seed Fund, University of Liverpool - ``Past and future of urban
    structures in Latin American cities''}. PI. \pounds8,887
\item[2017] \emph{Santander Bank} - Travel Grant. PI. \pounds1,000
\item[2014] \emph{FOSTER EU-funded (FP7)}. ``Workshop on Open Workflows''.
    Together with Thomas de Graaff. CoI. \euro2,150
\item[] \emph{GeoDa Center for Geospatial Analysis and Computation, Arizona
    State University}. ``Space in Hierarchical Linear Models using Python''.
    PI. \$18,000

\item[2007] \emph{Spanish Ministry of Education and Science}. ``University
    Staff Training Programme'' (in Spanish, ``Formaci\'{o}n de Personal
    Universitario'', FPU). Pre-Doctoral grant. 2007/10. \euro 48,000
%   \item[2005-06] \emph{Erasmus} Education Programme. Sponsor: European Commission.

%   \item[2004-05] \emph{Sercicio de Documentaci\'{o}n y Econom\'{i}a Aragonesa
%       (Service for Documentation and Economy of Arag\'{o}n}. Sponsor: Caja de
%       Ahorros de la Inmaculada.
%\item[2005-06] \emph{Regional Socieconomic Modeling in Support of Economc
%  Development Networks.} Co-Principal Investigtor.\\ Sponsor: Defense Logistics
%  Agency (\$1,200,000).

    \item[\textbf{Projects (as researcher)}]
\item[2009-2013] \emph{Migrant Diversity and Regional Disparity in Europe}. Peter
    Nijkamp (PI) and Jacques Poot (Co-PI).
    Post-doctoral researcher (June, 2012-March, 2014). \\ Sponsor: NORFACE research program on
    migration. \euro2,548,920

\item[2011-2013] \emph{Affordable Housing and Walkable Neighborhoods A
    National Urban Analysis}. Julia Koschinsky and Emily Talen (PI and Co-PI).
    Researcher (January-May, 2012). \\ Sponsor: U.S. Department of Housing and Urban Development. \$US 500,000

\item[2011-2013] \emph{Flexible Geospatial Visual Analytics and Simulation
    Technologies to Enhance Criminal Justice Decision Support Systems}. Luc
    Anselin and Serge Rey (PI and Co-PI).
    Researcher (January-December, 2011). \\ Sponsor: U.S. Department of Justice, National Institute of
    Justice, \$US 1.4 million

\item[2010] \emph{Estrategia de Zaragoza y su entorno en el horizonte 2020}
    Scholar. \\ Sponsor: Ebr\'{o}polis.

\item[2009-2012] \emph{Aspectos te\'{o}ricos y emp\'{i}ricos asociados al
    fen\'{o}meno de
    urban sprawl} ECO2009-09332. Scholar. \\ Sponsor: Ministry of Science and Innovation,
    Government of Spain. 42.900\euro

  \item[2007-2009] \emph{La distribuci\'{o}n del tama\~{n}o de las ciudades:
     regularidades emp\'{i}ricas y modelos te\'{o}ricos explicativos}
     SEJ2006-04893. Scholar. \\ Sponsor: Ministry of Science and Education, Government of Spain.
    34.485\euro



\end{cvlist}
%}}}1
  \begin{cvlist}{Publications}
  %{{{1
 %\item[\textbf{Refereed Journal Articles and Book Chapters}]
  %{{{2
%\item[2006] Rey, S.J. and L. Anselin ``Recent Advances in Software for Spatial Analysis in the 
 % Social Sciences.'' \emph{Geographical Analysis.} 38: 1-4.
\item[\textbf{Books}]

\item[\textit{2023}] Rey, S.; Arribas-Bel, D.; Wolf, L. J.
        ``Geographic Data Science with Python''. CRC Press.
        \texttt{https://geographicdata.science/book/}

%}}}2
\item[\textbf{Peer-reviewed journal articles}]
%{{{2

%{{{2
%{{{2
%{{{2
\item[\textit{2025}] Murphy, J., Mahabir, R., Phinn, S., Arribas-Bel, D.
        ``Navigating coastal resilience: Exploring population density and
        coastal distance dynamics along the gold coast''.
        \emph{Global Challenges \& Regional Science}, 3, 100019.
        \texttt{10.1016/j.gcrs.2025.100019}.
\item[\textit{2024}] Fleischmann, M., \& Arribas-Bel, D. 
  ``Decoding (urban) form and function using spatially explicit deep learning''.
  \emph{Computers, Environment and Urban Systems}, 112, 102147.
  \texttt{10.1016/j.compenvurbsys.2024.102147}.
\item[] Kenyon, G.E.; Arribas-Bel, D.; Robinson, C. 
  ``Extracting Features from Satellite Imagery to Understand 
  the Size and Scale of Housing Sub-Markets in Madrid''. 
  \emph{Land}, 13, 575. \texttt{10.3390/land13050575}.
\item[] Kenyon, G.E., Arribas-Bel, D., Robinson, C. et al. 
  ``Intra-urban house prices in Madrid following the financial crisis: 
  an exploration of spatial inequality''. 
  \emph{npj Urban Sustain} 4, 26. 
  \texttt{10.1038/s42949-024-00161-0}.

\item[\textit{2023}] Calafiore, A.; Samardzhiev, K.; Rowe, F.;
        Fleischmann, M.; Arribas-Bel, D.
        ``Inequalities in experiencing urban functions.
        An exploration of human digital (geo-)footprints''.
        \emph{Environment and Planning B - Urban Analytics and City Science}.\\
        \texttt{10.1177/23998083231208}.
\item[] Salat, H.; Carlino, D.; Benitez-Paez, F.; Zanchetta, A.;
        Arribas-Bel, D.; Birkin, M.
        ``Synthetic population Catalyst: A micro-simulated population of
        England with circadian activities''.
        \emph{Environment and Planning B - Urban Analytics and City Science}. \\
        \texttt{10.1177/23998083231203066}.
\item[\textit{}] Murphy, J.; Plater, A.; Bird, C.; Arribas-Bel, D.
        ``Spatial-temporal variability: characterisation of a beach system
        using high resolution radar data''.
        \emph{Frontiers in Marine Science}. Vol. 10. \\
        \texttt{10.3389/fmars.2023.1142077}.
\item[] Owen, D.; Arribas-Bel, D.; Rowe, F.
        ``Tracking the Transit Divide: A Multilevel Modelling Approach of Urban Inequalities
        and Train Ridership Disparities in Chicago''.
        \emph{Sustainability}, 15(11). \\
        \texttt{10.3390/su15118821}.
\item[\textit{2022}] Arribas-Bel, D.; Fleischmann, M.
        ``Spatial Signatures - Understanding (urban) spaces through form and function''.
        \emph{Habitat International}, 128. \\
        \texttt{10.1016/j.habitatint.2022.102641}.

\item[] Fleischmann, M.; Arribas-Bel, D.
        ``Geographical characterisation of British urban form and function using the spatial signatures framework''.
        \emph{Scientific Data}, 9, 546. \\
        \texttt{10.1038/s41597-022-01640-8}.

\item[] Rowe, F.; Calafiore, A.; Arribas-Bel, D.; Samardzhiev, K.;
        Fleischmann, M.
        ``Urban exodus? Understanding human mobility in Britain during the
        COVID-19 pandemic using Meta-Facebook data''.
        \emph{Population, Space and Place}, 29, e2637.\\
        \texttt{10.1002/psp.2637}.

\item[] Patias, N.; Rowe, F.; Arribas-Bel, D.
        ``Local urban attributes defining ethnically segregated areas across English cities: A multilevel approach''.
        \emph{Cities}, 132. \\
        \texttt{10.1016/j.cities.2022.103967}.

\item[] Samardzhiev, K.; Fleischmann, M.; Arribas-Bel, D.; Calafiore, A.; Rowe, F.
    ``Functional signatures in Great Britain: A dataset''.
    \emph{Data in Brief}, 43.
    \texttt{10.1016/j.dib.2022.108335}.

\item[] Comber, S.; Park, S.; Arribas-Bel, D.
        ``Dynamic-IMD (D-IMD): Introducing activity spaces to deprivation
        measurement in London, Birmingham and Liverpool''.
        \emph{Cities}, 127.
        \texttt{10.1016/j.cities.2022.103733}.

\item[] Chen, M.; Liu, Y.; Arribas-Bel, D.; Singleton, A.
        ``Assessing the value of user-generated images of urban surroundings
        for house price estimation''.
        \emph{Landscape and Urban Planning}, 226.
        \texttt{10.1016/j.landurbplan.2022.104486}.

\item[] Singleton, A.; Arribas-Bel, D.; Murray, J.; Fleischmann,
        M.
        ``Estimating generalized measures of local neighbourhood context from
        multispectral satellite images using a convolutional neural network''.
        \emph{Computers, Environment and Urban Systems}, 95.
        \texttt{10.1016/j.compenvurbsys.2022.101802}.
\item[\textit{2021}]
        Patias, N.; Rowe, F.; Arribas-Bel, D.
        ``Trajectories of neighbourhood inequality in Britain: Unpacking
        inter-regional socioeconomic imbalances, 1971-2011''.
        \emph{The Geographical Journal}. \texttt{10.1111/geoj.12420}.
\item[]
        Rey, S. J.; Anselin, L.; Amaral, P.; Arribas-Bel, D.; Cortes, R. X.;
        Gaboardi, J. D.; Kang, W.; Knaap, E.; Li, Z.; Lumnitz, S.; Oshan, T.
        M.; Shao, H.; Wolf, L. J.
        ``The PySAL Ecosystem: Philosophy and Implementation''.
        \emph{Geographical Analysis}.
        \texttt{10.1111/gean.12276}
\item[]
        Arribas-Bel, D.; Green, M.; Rowe, F.; Singleton, A.
        ``Open data products - A framework for creating valuable analysis
        ready data''.
        \emph{Journal of Geographical Systems}.
        \texttt{10.1007/s10109-021-00363-5}
\item[]
        Wolf, L. J.; Anselin, L.; Arribas-Bel, D.; Mobley, L. R.
        ``On Spatial and Platial Dependence: Examining Shrinkage in Spatially
        Dependent Multilevel Models''.
        \emph{Annals of the American Association of Geographers}.
        \texttt{10.1080/24694452.2020.1841602}
\item[]
    Alharbi, Y.; Arribas-Bel, D.; Coenen, F. ``Sustainable Development Goal
    Relational Modelling and Prediction: Introducing the SDG-CAP-EXT
    Methodology''. Journal of Data Intelligence.
\item[]
    Patias, N.; Rowe, F.; Cavazzi, S.; Arribas-Bel, D.
    ``Sustainable urban development indicators in Great Britain from 2001 to
    2016''.
    \emph{Landscape and Urban Planning}, 214. 0169-2046.
    \texttt{https://doi.org/10.1016/j.landurbplan.2021.104148}
\item[]
    Liu, Y.; Singleton, A.; Arribas-Bel, D.; Chen, M.
    ``Identifying and understanding road-constrained areas of interest (AOIs)
    through spatiotemporal taxi GPS data: A case study in New York City''.
    \emph{Computers, Environment and Urban Systems}, 86.
        \texttt{j.compenvurbsys.2020.101592}
\item[] Calafiore, A.; Palmer, G.; Comber, S.; Arribas-Bel, D.; Singleton, A.
        ``A geographic data science framework for the functional and
        contextual analysis of human dynamics within global cities''.
        \emph{Computers, Environment and Urban Systems}, 85.
        \texttt{j.compenvurbsys.2020.101539}
\item[\textit{2020}]
    Comber, S.; Arribas-Bel, D.; Singleton, A.; Dolega, L.
    ``Using Convolutional Autoencoders to Extract Visual Features of Leisure
    and Retail Environments''.
    \emph{Landscape and Urban Planning}, 202.
\item[]
    Thompson, R. N.; Hollingsworth, T. D; Isham, V.;
    Arribas-Bel, D.; Ashby, B.; Britton, T.; Challenor, P.;
    Chappell, L. H. K.; Clapham, H.; Cunniffe, N. J.;
    Dawid, A. P.; Donnelly, C. A.; Eggo, R. M.; Funk,
    S.; Gilbert, N.; Glendinning, P.; Gog, J. R.;
    Hart, W. S.; Heesterbeek, H.; House, T.; Keeling, M.;
    Kiss, I. Z.; Kretzschmar, M. E.; Lloyd, A. L.;
    McBryde, E. S.; McCaw, J. M.; McKinley, T. J.; Miller,
    J. C.; Morris, M.; O'Neill, P. D.; Parag, K. V.;
    Pearson, C. A. B.; Pellis, L.; Pulliam, J. R. C.; Ross,
    J. V.; Tomba, G. S.; Silverman, B. W.;
    Struchiner, C. J.; Tildesley, M. J.; Trapman, P.;
    Webb, C. R.; Mollison, D.; Restif, O.
    ``Key questions for modelling COVID-19 exit strategies''.
    \emph{Proceedings of the Royal Society B: Biological Sciences}.
    287(1932), 20201405. \texttt{10.1098/rspb.2020.1405}
\item[]
     Puente-Ajov\'{i}n, M.; Ramos, A.; Sanz-Gracia, F.; Arribas-Bel, D.
     ``How sensitive is city size distribution to the definition of city? The
     case of Spain''. Volume 197.
     \emph{Economics Letters}. DOI: \texttt{10.1016/j.econlet.2020.109643}
\item[] Franklin, R.; Houlden, V.; Robinson, C.; Arribas-Bel, D.; Delmelle,
    E. C.; Dem\v{s}ar, U.; Miller, H. J.; O'Sullivan, D.
    ``Who Counts? Gender, Gatekeeping, and Quantitative Human Geography''
    \emph{The Professional Geographer}.
\item[] Chen, M., Fahrner, D., Arribas-Bel, D. \& Rowe, F. ``A reproducible
    notebook to acquire, process and analyse satellite imagery'',
    \emph{REGION},
    7(2), pp. R15-R46. DOI: \texttt{10.18335/region.v7i2.295}
\item[] 
    Olson, A. W.; Zhang, K.; Calderon-Figueroa, F.; Yakubov, R.; Sanner, S.;
    Silver, D.; Arribas-Bel, D.
    ``Classification and Regression via Integer Optimization for Neighborhood
    Change''.
    \emph{Geographical Analysis}.
\item[] 
    Chen, M.; Arribas-Bel, D.; Singleton, A. ``Quantifying
    characteristics of the local urban environment through geotagged Flickr
    photographs and image recognition''. \emph{International Journal of
    Geo-Information}, 9, 264. \texttt{10.3390/ijgi9040264}
\item[] 
    Lumnitz, S; Arribas-Bel, D.; Cortes, R. X.; Gaboardi, J. D.; Griess, V.;
    Kang, W.; Oshan, T. M.; Wolf, L.; Rey, S.. ``splot - visual
    analytics for spatial statistics''. \emph{Journal of Open Source Software},
    5(47), 1882,
    \texttt{10.21105/joss.01882}
\item[\textit{2019}] 
    Arribas-Bel, D; Garcia-Lopez, M.-A. Garcia-Lopez; Viladecans-Marsal, E.
    ``Building(s and) cities: Delineating urban areas with a machine learning
    algorithm''.
    \emph{Journal of Urban Economics}.
    \texttt{10.1016/j.jue.2019.103217}
\item[] 
    Comber, S; Arribas-Bel, D; Singleton, A; Dong, G; Dolega, L.
    ``Building Hierarchies of Retail Centers Using Bayesian Multilevel
    Models''.
    \emph{Annals of the American Association of Geographers}.
    \texttt{10.1080/24694452.2019.1667219}
\item[] 
    Singleton, A; Arribas-Bel, D. ``Geographic Data Science''.
    \emph{Geographic Analysis}. \texttt{10.1111/gean.12194}
\item[] 
    Stubbings, P.; Peskett, J.; Rowe, F.; Arribas-Bel, D.
    ``A Hierarchical Urban Forest Index Using Street-Level Imagery and Deep
    Learning''.
    \emph{Remote Sensing}, 11(12). \texttt{10.3390/rs11121395}
\item[] 
    Arribas-Bel, D. ``A course on Geographic Data Science''.
    \emph{The Journal of Open Source Education}, 2(14), 42. \texttt{10.21105/jose.00042}
\item[] 
    Comber, S.; Arribas-Bel, D. ``Machine learning innovations in address
    matching: A practical comparison of word2vec and CRFs''.
    \emph{Transactions in GIS}. 23, (2): pp. 334-348.
\item[] 
    Liu, Y.; Singleton, A.; Arribas-Bel, D. ``A principal component analysis
    (PCA)-based framework for automated variable selection in geodemographic
    classification''.
    \emph{Geo-spatial Information Science}.
    \texttt{10.1080/10095020.2019.1621549}
\item[] 
    Davies, A. E.; Dolega, L.; Arribas-Bel, D. ``Buy online collect in-store:
    Exploring grocery click \& collect using a national case study''.
    \emph{International Journal of Retail and Distribution Management}.
\item[] 
    Chen, M; Arribas-Bel, D.; Singleton, A. ``Understanding the
    dynamics of urban areas of interest through volunteered geographic
    information''. \emph{Journal of Geographical Systems}.
\item[] 
    Dong, G.; Alexiou, A.;Arribas-Bel, D.; Wolf, L.J. ``Inferring
    neighbourhood quality with property transaction records by using a locally
    adaptive spatial multi-level model''. 
    \emph{Computers, Environment and Urban Systems}.
\item[\textit{2018}] 
    Arribas-Bel, D.; Reades, J. ``Geography and Computers: Past, present, and future''.
    \emph{Geography Compass}.
\item[] 
    Arribas-Bel, D.; Bakens, J. ``Use and Validation of Location-Based
    Services in Urban Research: An Example with Dutch Restaurants''.
    \emph{Urban Studies}, 56(5): 868:884.
\item[] 
    Arribas-Bel, D.; Bakens, J. ``Spatial dynamics of cultural diversity 
    in the Netherlands''.
    \emph{Environment and Planning B - Urban Analytics and City Science}.
    \texttt{doi: 10.1177/2399808318783748}
\item[\textit{2017}] 
Arribas-Bel, D.; Tranos, E. ``Characterizing the Spatial Structure(s) of
Cities 'on the fly': the Space-Time Calendar''.
\emph{Geographical Analysis}, 50(2): 162-181. \texttt{doi:10.1111/gean.12137}

\item[] 
Gerritse, M.; Arribas-Bel, D. ``Concrete agglomeration benefits: do roads
improve urban connections or just attract more people?''. \emph{Regional
Studies}, 52(8): 1134-1149.
\item[] 
Wolf, L.; Anselin, L.; Arribas-Bel, D. ``Stochastic Efficiency of Bayesian
MCMC in Spatial Econometric Models: An Empirical Comparison''.
\emph{Geographical Analysis}, 50:97-119. \texttt{doi:10.1111/gean.12135}
%}}}2%{{{2
\item[] Arribas-Bel D., Patino J.E., Duque J.C. ``Remote
    sensing-based measurement of Living Environment Deprivation: Improving
    classical approaches with machine learning''. \emph{PLOS ONE}. 12(5): e0176684.
\item[] Comber, S., Arribas-Bel D. ``'Waiting on the train': The
    anticipatory (causal) effects of Crossrail in Ealing''. \emph{Journal of
    Transport Geography}. Vol. 64: 13-22.
%}}}2%{{{2
\item[\textit{2016}] Arribas-Bel, D., Nijkamp, P. and Poot, J. ``How
    diverse can measures of segregation be? Results from Monte Carlo
    simulations of an agent-based model''. \emph{Environment and Planning A},
    48 (10): 2046-2066.
%}}}2 }}}1
%{{{2
\item[] Folch, D.; Arribas-Bel, D.; Koschinsky, K; Spielman,
    S. ``Spatial Variation in the Quality of American Community Survey
    Estimates''. \emph{Demography}, 53(5): 1535-1554.
%}}}2 }}}1
%{{{2
\item[2015] Arribas-Bel, D.; Kourtit, K.; Nijkamp, P. ``Cultural Diversity and
    Urban Buzz''. \emph{Environment and Planning C -- Government and
    Policy}, 33: 1-17.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D.; Gerritse, M. ``From manufacturing
    belt, to rust belt, to college
    country - A Visual Narrative of the US Urban Growth''.
    \emph{Environment and Planning A}, 47(6): 1241-1253.
%}}}2 }}}1

\item[] Arribas-Bel, D.; Ramos, A.; Sanz Gracia, F. ``The size distribution of employment centers within the U.S. Metropolitan Areas''.
    \emph{Environment and Planning B: Planning and Design}, 42: 23-39.
    %}}}2 }}}1

\item[] Arribas-Bel, D.; Kourtit, K.; Nijkamp, P.; Steenbruggen, J. ``Cyber Cities: Social Media as a Tool for Understanding Cities''.
\emph{Applied Spatial Analysis and Policy}, 8(3): 231-247.
    %}}}2 }}}1

%{{{2
\item[2014] Arribas-Bel, D.; Sanz Gracia, F. ``The Validity of the Monocentric
    City Model in a Polycentric Age: US Metropolitan areas in 1990, 2000 and 2010''.
    \emph{Urban Geography}, 35(7): 980-997.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D. ``Accidental, Open and Everywhere: Emerging Data Sources
    for the Understanding of Cities''. \emph{Applied Geography}, 49: 45-53.
%}}}2 }}}1

\item[] Kourtit, K.; Nijkamp, P.; Arribas-Bel, D. ``Migrant
    Entrepreneurs as Urban 'Health Angels' -- Contrasts in Growth Strategies''.
    \emph{International Planning Studies}.
%}}}2 }}}1

%{{{2
\item[2013] Arribas-Bel, D., Schmidt, C. R.
    ``Self-organizing maps and the US urban spatial structure''
    \emph{Environment and Planning B: Planning and Design}, 2: 362-371.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D., Kourtit, K.,
    Nijkamp, P. ``Benchmarking of World cities through self-organizing maps''
    \emph{Cities}, 31: 248-257.
%}}}2 }}}1

%{{{2
\item[] Anselin, L., Arribas-Bel, D.
    ``Spatial fixed effects and spatial dependence''
    \emph{Papers in Regional Science} 92(1): 3-17.
%}}}2 }}}1

%{{{2
\item[] Amaral, P. V.,  Anselin, L., Arribas-Bel, D.
    ``Testing for spatial error dependence in probit models''
    \emph{Letters in Spatial Resource and Sciences} 6(2): 91-101.
%}}}2 }}}1

%{{{2
\item[2012] Arribas-Bel, D.; Koschinsky, J. and Amaral, P. V. ``Improving the
    Multi-Dimensional Comparison of Simulation Results: A Spatial
    Visualization Approach'' \emph{Letters in Spatial and Resource Sciences},
    5(2): 55-63.
%}}}2 }}}1

%{{{2
\item[] Kourtit, K.,
    Nijkamp, P., Arribas-Bel, D. ``Smart Cities Perspective - a Comparative
    European Study by Means of Self-Organizing Maps''
    \emph{Innovation: The European Journal of Social Science Research},
    25(2):229-246.
%}}}2 }}}1

\item[] Arribas-Bel, D., Sanz-Gracia, F.,
    Ximenez-de-Emb\'{u}n, D. P. ``Kangaroos, cities and space: a first
    approach to the Australian urban system''
    \emph{R\'{e}gion et D\'{e}veloppement}, 36: 165-187.
%}}}2 }}}1

%{{{2
\item[] Kourtit, K., Arribas-Bel, D.,
    Nijkamp, P. ``High Performers in Complex Spatial Systems: A
    Self-Organizing Mapping Approach with Reference to The Netherlands''
    \emph{The Annals of Regional Science}, 48(2):501-527.
%}}}2 }}}1

%{{{2
\item[2011] Arribas-Bel, D.; Nijkamp, P. and Schoelten, H. ``Multidimensional urban
    sprawl in Europe: a self-organizing map
    approach'' \emph{Computers, Environment and Urban Systems}, 35(4):265 -
    275.
%}}}2 }}}1

%{{{2
\item[] Rey, S.J.; Anselin, L.; Folch, D. C.; Arribas-Bel, D.;
    Sastr\'{e} Guti\'{e}rrez, M. L.  and Interlante, L. ``Measuring Spatial
    Dynamics in Metropolitan Areas''. \emph{Economic Development
    Quarterly}, 25(1): 54-64.
%}}}2 }}}1

\item[\textbf{Conference Proceedings}]
\item[\textit{2026}] 
    Wagg, D.; Malleson, N.; Beltran, A.; Tipuric, M.; Arribas-Bel, D.
    ``Using Earth Observation Informed Agent-Based Models to build a Scenario
    Planning Digital Twin for Local Energy Policies''.
    EGU26-22325. \texttt{10.5194/egusphere-egu26-22325}.
\item[\textit{2021}] 
    Alharbi, Y.; Coenen, F.; Arribas-Bel, D. ``Sustainable Development Goals
    Monitoring and Forecasting using Time Series Analysis''. Delta 2021 - 2nd
    International Conference on Deep Learning Theory and Applications.

\item[\textit{2020}] 
    Alharbi, Y.; Coenen, F.; Arribas-Bel, D. ``Sustainable Development Goal
    Relational Modelling: Introducing the SDG-CAP Methodology''. International
    Conference on Big Data Analytics and Knowledge Discovery, Bratislava,
    Slovakia, 14 Sep 2020 - 17 Sep 2020. Lecture Notes in Computer Science.
    Springer Nature. 12393: 183-196.
\item[] 
    Alharbi Y, Arribas-Bel D, Coenen F. ``Sustainable Development Goal
    Relational Modelling: Introducing the SDG-RMF Methodology'', in AI for
    Social Good Workshop. IJCAI Workshop on AI for Social Good.

\item[\textit{2019}] 
    Alharbi Y, Arribas-Bel D, Coenen F. 
    ``Sustainable Development Goal Attainment Prediction: A Hierarchical
    Framework using Time Series Modelling'', in Proceedings of the 11th
    International Joint Conference on Knowledge Discovery, Knowledge
    Engineering and Knowledge Management - KDIR, 297-304, Vienna,
    Austria.

%}}}2
\item[\textbf{Other academic articles}]
%{{{2
\item[\textit{2026}] Arribas-Bel, D., Franklin, R. ``Satellite Salvation? Why
        satellite imagery is (part of) the answer to our urban data needs''.
  \emph{Environment and Planning B: Urban Analytics and City Science}, 53(5).
  \texttt{10.1177/23998083261456945}.
\item[\textit{2026}] Beecham, R., Arribas-Bel, D. ``Open spatial science as
        routine practice: Urban Data/Code contributions from GISRUK 2024''.
  \emph{Environment and Planning B: Urban Analytics and City Science}, 53(3).
  \texttt{10.1177/23998083261431404}.
\item[\textit{2025}] Arribas-Bel, D., Metzler, B., \& Lynn, S. "AI in land use".
  \emph{Environment and Planning B: Urban Analytics and City Science}, 52(2).
  \texttt{10.1177/23998083251316384}.
\item[\textit{2024}] Malleson, N., Franklin, R., Arribas-Bel, D., Cheng, T., \& Birkin, M. (2024). 
  ``Digital twins on trial: Can they actually solve wicked societal problems and 
  change the world for better?'' 
  \emph{Environment and Planning B: Urban Analytics and City Science}, 51(6), 1181-1186.
  \texttt{10.1177/23998083241262893}.
\item[] Arribas-Bel, D., \& Fleischmann, M. "In praise of (spatial) bundles".
    \emph{Environment and Planning B: Urban Analytics and City Science},
    \texttt{23998083231224151}.
\item[\textit{2021}] Arribas-Bel, D., Alvanides, S., Batty, M., Crooks, A., See, L., \&
    Wolf, L. ``Urban data/code: A new EP-B section''. \emph{Environment and
    Planning B - Urban Analytics and City Science}, 48(9), 2517-2519.
    \texttt{10.1177/23998083211059670}.
\item[2020] Rowe, F., Maier, G., Arribas-Bel, D., \& Rey, S.. ``The Potential of
    Notebooks for Scientific Publication, Reproducibility and Dissemination''.
    \emph{REGION}, 7(3), E1-E5. DOI: \texttt{10.18335/region.v7i3.357}.
\item[\textit{2018}] 
    Arribas-Bel, D.; Tranos, E. ``Big Urban Data: Challenges and Opportunities
    for Geographical Analysis''. Editorial. \emph{Geographical Analysis}.
    \texttt{doi:10.1111/gean.12157}.
%{{{2
\item[\textit{2017}] Harris, R., O'Sullivan, D., Gahegan, M., Charlton, M.,
    Comber, L., Longley, P., Brunsdon, C., Malleson, N., Heppenstall, A.,
    Singleton, A., Arribas-Bel, D,. Evans, A. ``More bark than bytes?
    Reflections on 21+ years of geocomputation''. \emph{Environment and
    Planning B: Urban Analytics and City Science}. 44(4): 598-617.
%}}}2
%{{{2
\item[2016] Arribas-Bel, D. ``London: The Information Capital: 100 Maps and Graphics That Will Change How You View the City. James Cheshire and Oliver Uberti. London: Particular Books (Penguin), 2014.''.
    \emph{Papers in Regional Science}, 96(1): 223-224.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D. ``Geocomputation: A Practical Primer, edited by Chris Brunson and Alex Singleton.''.
    \emph{Journal of Regional Science}, 56(1): 176-178.
%}}}2 }}}1

%{{{2
\item[2015] Arribas-Bel, D. ``Review of \textit{Simulation of Complex Systems
    in GIS}, by Patrice Laglois''.
    \emph{Environment and Planning B: Planning and Design}, 42: 564-567.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D. ``The spoken postcodes''.
    \emph{Regional Studies, Regional Science}, 2(1): 457-460.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D., Graaff, T. ``WooW-II: Workshop on open workflows''.
    \emph{REGION}, 2(2): R1-R2.
%}}}2 }}}1

%{{{2
\item[2014] Arribas-Bel, D. ``Spatial Data, Analysis, and Regression - A mini course''.
    \emph{REGION}, 1(1): R1.
%}}}2 }}}1

%{{{2
\item[2012] Arribas-Bel, D. and Gerritse, M. ``Monocentricity? Commuting flows
    visually.'' \emph{Featured Graphic, Environment and Planning A}. 44(9):
    2041 - 2042.
%}}}2 }}}1

\item[\textbf{Book chapters}]

\item[2024] Arribas-Bel, D., Graser, A.  ``Geographic data science: a manifesto''.
        In A Research Agenda for Spatial Analysis. 
        Edited by Levi John Wolf, Richard Harris, and Alison Heppenstall.
        Edward Elgar Publishing.
        \texttt{ISBN: 978 1 80220 322 6}.

\item[2023] Arribas-Bel, D., Rowe, F., Chen, M., \& Comber, S. ``An image library:
        The potential of imagery in (quantitative) social sciences''. In Handbook
        of Spatial Analysis in the Social Sciences (pp. 528-543).
        Edward Elgar Publishing. DOI: \texttt{10.4337/9781789903942}

\item[2020] Boeing, G.; Arribas-Bel, D. ``GIS and Computational
    Notebooks''. \emph{The Geographic Information Science \& Technology Body of
    Knowledge (1st Quarter 2021 Edition)}, John P. Wilson (Ed.). DOI:
    \texttt{10.22224/gistbok/2021.1.2}

\item[2018] Arribas-Bel, D. Statistics, Modelling, and Data Science.
    In \textit{Digital Geographies} (Ash, J., Kitchin, R. and Leszczynski, A.,
    eds.), pp. 129-140. SAGE.

\item[] de Graaff, T., Arribas-Bel, D., \& Ozgen, C. Demographic Aging and
    Employment Dynamics in German Regions: Modeling Regional Heterogeneity. In
    \textit{Modelling Aging and Migration Effects on Spatial Labor Markets}
    (pp. 211-231). Springer, Cham.

%{{{2
\item[2017] Arribas-Bel, D., T. de Graaff and S.J. Rey.
    ``Looking at John Snow's cholera map from the XXIst century: a practical
    primer on Reproducibility and Open Science''. In:  \textit{Regional Research Fontiers} (R.W. Jackson and P.
    Schaeffer, eds.). Springer.
%}}}2 }}}1
%{{{2
\item[2013] Kourtit, K.; Nijkamp, P.; Arribas-Bel, D.  ``The Creative Urban
    Diaspora Economy: A Disparity Analysis among Migrant Entrepreneurs.'' In:
    \textit{Handbook of Research Methods and Applications in Urban Economies}
    (Kresl, P., Vaughan, C.P, Sobrino, J., eds.).
%}}}2 }}}1

\item[\textbf{Other}]
%{{{2
\item[2025] Arribas-Bel, D. ``El papel de la geograf\'ia en la revoluci\'on de datos: ejemplos
        desde la ciencia de datos geogr\'aficos''. In: \textit{Geograf\'ia,
        cambio global y vulnerabilidad territorial. Herramientas para el
conocimiento de un mundo en transformaci\'on permanente}. Universidad de La
Laguna (Spain). Available at:
        \url{http://riull.ull.es/xmlui/handle/915/42264}
\item[2024] The Alan Turing Institute. ``Geospatial AI for Land Use, by The
        Alan Turing Institute''. Independent report. Commissioned by the Geospatial
        Commission. Principal Investigator.
        \url{https://www.gov.uk/government/publications/geospatial-ai-for-land-use-by-the-alan-turing-institute/geospatial-ai-for-land-use-by-the-alan-turing-institute}
\item[2021] Darlington-Pollock, F.; Arribas-Bel, D.; Rowe, F. ``What do 'left
    behind' areas looklike over time?''. Consultancy report for the Left
    Behind Neighbourhoods Local Trust. \url{https://localtrust.org.uk}
\item[2019] Arribas-Bel, D.  ``Imagery: A better 'picture' of the city''.
    Contributed post on the Connected Cities Catapult blog. Available at:
    \url{https://cp.catapult.org.uk/2019/12/13/imagery-a-better-picture-of-the-city/}
\item[] Rowe, F.; Patias, N.; Arribas-Bel, D.  ``Policy Brief:
    Neighbourhood Change and Trajectories of Inequality in Britain,
    1971-2011''. \textit{UK2070 Commission}.
\item[] Arribas-Bel, D.  ``Six 15-minute walks capture the diversity,
    history of Houston neighborhoods''. \textit{Urban Edge Blog}. Kinder Insitute for Urban
    Research, Rice University. Available at
    \url{https://kinder.rice.edu/urbanedge/2019/04/08/maps-six-15-minute-walks-capture-diversity-history-houston-neighborhoods}
\item[2015] Arribas-Bel, D.  ``Does Twitter make us view cities differently?'' In:
    \textit{University of Birmingham Tumblr blog. May 15th, 2015.}
    Available at
    \url{http://unibirmingham.tumblr.com/post/119013810163/does-twitter-make-us-view-cities-differently}
%}}}2
%{{{2
\item[2014] Arribas-Bel, D.  ``Open Workflows for Open Regional Science'' In:
    \textit{NARSC Newsletter. Issue 1, No.2, June.}
    Available at
    \url{http://www.narsc.org/newsite/wp-content/uploads/2014/06/NARSCNewsJune2014-Final2.pdf}
%}}}2 }}}1
%{{{2
\item[2013] Arribas-Bel, D.  ``Cultural diversity and increased urban buzz'' In:
    \textit{Migration: New Developments. Spring 2013}
    NORFACE Research Programme on Migration. Available at
    \url{http://www.norface-migration.org/files/NORFACE_2013_single.pdf}
%}}}2 }}}1


\item[\textbf{Working Papers}]

%{{{2
%{{{2
\item[2013] Arribas-Bel, D.; Florax, R. ``Heterogeneity and Dependence in
    Geo-Referenced Micro Data: Random Effects vs True Contagion''.
%}}}2 }}}1

%{{{2
\item[] Arribas-Bel, D.; Sanz Gracia, F. ``On the existence of
    agglomeration shadows at the metropolitan level''.
%}}}2 }}}1

%{{{2
\item[2012] Anselin, L; Amaral, P. V.; Arribas-Bel, D. ``Technical Aspects of
    Implementing GMM Estimation of the Spatial Error Model in PySAL and GeoDaSpace''.
    GeoDa Center Technical Report available at
    \url{https://geodacenter.asu.edu/drupal_files/sperrorgmm_wp2.pdf}
%}}}2 }}}1

\end{cvlist}


 \begin{cvlist}{Research Visits}
 %{{{1
 \item[2023] CEMFI. Madrid (Spain). External Faculty.
 \item[2022] CEMFI. Madrid (Spain). External Faculty.
 \item[2021] CEMFI. Madrid (Spain). External Faculty.
 \item[2019] Research in Spatial Economics (Rise) group. Universidad
     EAFIT. Medellin (Colombia). Visitor.

 \item[] Instituto Nacional de Pesquisas Espaciais (INPE, National
     Institute for Space Research). S\~ao Jos\'e dos Campos (Brazil). Visitor.

 \item[] Instituto de Pesquisa Ec\^onomica Aplicada (IPEA, Institute of
     Applied Economic Research). Brasilia (Brazil). Visitor.

 \item[] Centro de Desenvolvimento e Planejamento Regional da UFMG (CEDEPLAR,
     Centre for Development and Regional Planning). Universidade Federal de
     Minas Gerais. Bello Horizonte (Brazil). Visitor.

 \item[2018] Center for Geospatial Sciences, University of California,
     Riverside. Riverside (USA). Visitor.

 \item[2017] Center for Spatial Data Science, University of Chicago. Chicago
     (USA). Visitor.

 \item[] Spatial Structures in the Social Sciences, Brown University.
     Providence (USA). Visitor.

\item[2015] Kinder Institute for Urban Research, Rice University. Houston (USA).
     July-August. Visiting scholar.

\item[2014] Department of Economics, University of Houston. Houston (USA).
     June-August. Visiting scholar.

\item[2011] Department of Spatial Economics, The Faculty of Economics and
     Business Administration, Vrije Universiteit. Amsterdam (The Netherlands).
     July-August. Visiting researcher.

 \item[2010] Department of Spatial Economics, The Faculty of Economics and
     Business Administration, Vrije Universiteit. Amsterdam (The Netherlands).
     September. Visiting PhD student.
 
\item[] GeoDa Center for Geospatial Analysis and Computation, Arizona
    State University. Tempe, AZ (USA), March-May. Visiting PhD student.
 
 \item[2009] Department of Spatial Economics, The Faculty of Economics and
     Business Administration, Vrije Universiteit. Amsterdam (The Netherlands).
     September-December. Visiting PhD student.

\item[2008-09] GeoDa Center for Geospatial Analysis and Computation, Arizona
    State University. Tempe, AZ (USA), August-June. Visiting PhD student.
  \end{cvlist}

 \begin{cvlist}{Invited Lectures}
\item[\textbf{Keynote speeches}]

\item[2026] Arribas-Bel, D. ``Understanding Cities with New Forms of Data''.
        SPACERAISE summer school, Grand Sasso Science Institute. L'Aquila
        (Italy).
\item[2022] Arribas-Bel, D. ``Making it easy for Regional Scientists to
        consider (urban) form \& function''.
    Spatial Economic Analysis Lecture. Regional Science Association
    International, British and Irish Section. July. Stirling (UK).
\item[2021] Arribas-Bel, D. ``El papel de la Geograf\'ia en la revoluci\'on de datos:
    ejemplos desde la Ciencia de Datos Geogr\'aficos'''. XXVII Congreso de la
    Asociaci\'on Espa\~nola de Geograf\'ia. December. Tenerife (Spain).
\item[] Arribas-Bel, D. ``Building 'Geographic Data Science\ldots'''.
    International Conference on Geospatial Information Sciences. November.
    Mexico.
\item[] Arribas-Bel, D. ``Building 'Geographic Data Science\ldots'''.
        Geoinformation Science Symposium (virtual). October. Indonesia.

\item[\textbf{Seminars}]
%{{{1 
\item[2026] Arribas-Bel, D. ``Embeddings for the rest of us''.
        Universidad de Zaragoza. June.
\item[] Arribas-Bel, D. ``Making satellites more useful, usable and used
        in social research and policy''.
        Universidad de Zaragoza. June.
\item[] Arribas-Bel, D. ``Making satellites more useful, usable and used
        in social research and policy''. University of Leeds. June.
\item[2025] Arribas-Bel, D. ``The case for satellite imagery in social science
        and policymaking". Chinese Academy of Sciences. Beijing (China). May.
\item[] Arribas-Bel, D. ``The case for satellite imagery in social science
        and policymaking". Southwest University. Chongqing (China). May.
\item[2023] Arribas-Bel, D. ``Decoding urban form and function in Great Britain".
        IOER Forum. Leibniz Institute of Ecological Urban and Regional Development.
        November.
\item[] Arribas-Bel, D. ``Decoding urban form and function in Great
        Britain''. Economic Geography and Spatial Economics Seminar Series.
        London School of Economics. October.
\item[] Arribas-Bel, D. ``Urban Grammar - Decoding the socio-economic
        landscape with satellite imagery''. Workshop on Migration, Climate
        Change and Economic Development. Universidad de Zaragoza. September.
\item[] Arribas-Bel, D. ``Decoding the Socio-Economic landscape with
        satellite imagery''. Bank of England. July.
\item[] Arribas-Bel, D. ``Learning from Deep Learning - Lessons from using
        computer vision to identify (urban) form and function in open data
        satellite imagery''. AI and Sustainable Cities workshop. The Alan
        Turing Institute, UCL \& QMUL workshop. June.
\item[] Arribas-Bel, D. ``Measuring (even) better the Urban-Rural
        continuum''. JRC Webinar Series. Future of Cities. Online. April.
\item[] Arribas-Bel, D. ``Developing detailed, consistent and scalable
        characterisations of urban form \& function''. Masters Gathering.
        Industrial Technology Research Institute, Taiwan (online). April.
\item[2022] Arribas-Bel, D. ``Making it easy for regional scientists to
        consider (urban) form \& function''. Economic Data Science Seminar
        Series. Office for National Statistics. November.
\item[] Arribas-Bel, D. ``Open by Default - Developing reproducible,
        computational research''. Royal Statistical Society, Merseyside
        chapter. Session on open data sources. June.
\item[] Arribas-Bel, D. ``Urban Analytics@Turing''. Brown bag series. Mansueto
        Institute for Urban Innovation. University of Chicago. May.
\item[2021] Arribas-Bel, D. ``Building 'Geographic Data Science\ldots'''.
    Diplomado en An\'alisis de Datos para las Ciencias Sociales (remote). Universidad de
    Caldas. Colombia.
\item[] Arribas-Bel, D. ``Geographic Data Science: \textit{why, what,
    how}''. HM Land Registry Data Science seminars.
 \item[] Arribas-Bel, D. ``(Urban) Form \& Function in Great Britain''.
     Urban Analytics monthly meetup (remote). Alan Turing Institute (UK).
 \item[] Arribas-Bel, D. ``Infusing our understanding of cities with
     Geographic Data Science'' (remote). ETH Zurich (Switzerland).
 \item[    ] Arribas-Bel, D. ``Spatial Signatures -- \textit{Understanding
     (urban) spaces through form and function}'' (remote). ESRC Urban Big Data Centre
     seminar series. University of Glasgow. Glasgow (UK).
 \item[2020] Arribas-Bel, D. ``Building 'Geographic Data Science\ldots' ''. MSc
         in Economics seminar, Universidad de San Andr\'{e}s (Argentina).
         Online. November.
 \item[] Arribas-Bel, D. ``Urban Analytics - Maximising the value of big
     data for enhanced urban policy making''. Building Smart Cities with
     Citizens and for the Public Good: A Symposium. Organised by the Heseltine
     Institute, University of Liverpool. Liverpool. March.
 \item[2019] Arribas-Bel, D. ``Using New Forms of Data \& Machine Learning to 
     Understand Cities''. Innovation LAB seminar series, OECD. Paris (France).
     December.
 \item[] Arribas-Bel, D. ``Images as (policy-ready) data''. Acto Anual de
     Pol\'{i}tica Regional y Fondos Europeos en Espa\~{n}a (Annual Event for
     Regional Policy and European Funds in Spain). Madrid (Spain). November.
 \item[] Arribas-Bel, D. ``Building(s and) Cities''. MacArthur Foundation
     workshop on Urban Modelling \& Complexity Science. Centre for Advanced
     Spatial Analysis, University College London. London (UK). September.
\item[] Arribas-Bel, D. ``Infusing Urban Analytics with Geographic Data
    Science''. Urban Analytics at the interface between environment, human
    health and behaviour workshop. Tongji University (China). July.
\item[] Arribas-Bel, D. ``Urban Analysis with Geographic Data Science and
    New Forms of Data''. Instituto Nacional de Pesquisas Espaciais
    (INPE) (Brazil). March.
\item[] Arribas-Bel, D. ``Infusing Urban and Regional Policy with
    Geographic Data Science''. Instituto de Pesquisa Economica Aplicada
    (IPEA) (Brazil). March.
\item[] Arribas-Bel, D. ``Infusing Urban and Regional analysis
    with Geographic Data Science''. CUSP Seminars, King's College London.
    London (UK). January.
\item[] Arribas-Bel, D. ``Accessing \& Visualizing Satellite Data''. Workshop
    on Ocean and
    Coastal Monitoring and Modelling for Coastal Zone Management. Commonweath
    Marine Economies Programme. St. Vincent \& Grenada. January.
\item[2018] Arribas-Bel, D. ``Infusing Urban and Regional analysis
with Geographic Data Science''. University of Toronto, Toronto (Canada).
November.
\item[] Arribas-Bel, D. ``Infusing Urban \& Regional work with New Forms
    of Data''. OECD, Paris (France). September.
\item[] Arribas-Bel, D. ``Geographic Data Science - \textit{What, why, and
    how}''. 300,000Km/s, Barcelona (Spain). March.
\item[] Arribas-Bel, D. ``An Updatable Index of Neighborhood
    Desirability''. IEB Seminars, Universitat de Barcelona (Spain). February.
\item[] Arribas-Bel, D. ``New methods for new data? A few urban
    examples''. Data Science Seminars. ShopDirect, Liverpool. January.
\item[2017] Arribas-Bel, D. ``Towards a Geographic Data Science that Works for
    Everyone''. Spatial Data Science Conference. CARTO HQ, Brooklyn. December.
\item[] Arribas-Bel, D. ``The Spatial Structure of Cities Through The Lens
    Of New Forms Of Data''. CASA Seminars. Centre for Advanced Spatial
    Analysis. University College London.  November.
\item[] Arribas-Bel, D. ``Looking at Cities with New Lenses''. Roxby
    Centenary Lecture, University of Liverpool. November.
\item[] Arribas-Bel, D. ``Bringing new forms of data to the study of cities''. 
    UK Data Service Webinar. February.
\item[] Arribas-Bel, D. ``Remote Sensing-Based Measurement of Living
    Environment Deprivation - Improving Classical Approaches with Machine Learning''. 
    GVC/City REDI Seminar Series, University of Birmingham. (Birmingham, UK). February.
\item[] Arribas-Bel, D. ``Bringing New Forms of Data to the Study of Cities''. 
    Ritsumeikan University (Kyoto, Japan). January.
\item[2016] Arribas-Bel, D. ``Smart Cities - Examples, Opportunities and
    Challenges from Urban Research''. \textit{Smart Cities: myth or reality?}
    event held by the Telefonica Chair on Smart Cities and the IEB. University
    of Barcelona (Spain). January.
\item[2015] Arribas-Bel, D. ``The (geo)data revolution and the need for
    (Geographic) Data Science''. Remote lecture for the postgraduate course 
    Research Design in Urban Science, coordinated by Professor Marina Alberti.
    University of Washington (US). October.

\item[] Arribas-Bel, D. ``New approaches to measure the spatial
    structure(s) of cities''. Geospatial Big Data seminars.
    University College London (UK). March.

\item[2014] Arribas-Bel, D. ``Seeing cities through the lens of new (big) data
    -- Some examples''.
    University of Liverpool (UK). December.

\item[] Arribas-Bel, D. ``Seeing cities through the lens of new (big)
    data''.
    Institute for Employment Research (IAB). Nuremberg (Germany). September.

\item[] Arribas-Bel, D. ``Spatial Analysis \& Spatial Regression'' 
    Third year module in the Bachelor in Economics' Minor in Geography. Two
    lectures (3h).
    University of Utrecht (Netherlands). February.

\item[] Arribas-Bel, D. ``New data \& old Regional Science --
    Some examples'' GeoDa Center Brownbag series,
    Arizona State University (USA). February.

\item[] Arribas-Bel, D. ``Agglomeration Lights and Shadows within
    metropolitan areas -- US Cities in 2000'' Department of Global Economics \&
    Management internal seminars,
    University of Groningen (Netherlands). February.

\item[2012] Arribas-Bel, D. ``GeoDaSpace: advanced spatial econometrics made
    easy''. V Spatial Econometrics Seminar in honour of Jean Paelink,
    Universidade de Coimbra (Portugal). October.

\item[] Arribas-Bel, D.; Malizia, N. ``An introduction to R'' Graduates
    for Integrative Society and Environment Research (GISER), Arizona State
    University. March.

\item[2011] Arribas-Bel, D. ``Studying urban polycentricity in the US with
    spatial analysis methods'' European Investment Bank. July.

\item[2007] Arribas-Bel, D. ``45 minutes on Geographical and Urban Economics''
  Bremen International Graduate School of Social Sciences. December.

  \end{cvlist}

\begin{cvlist}{Conferences and Events}

\item[\textbf{Organization}]

\item[2025] \textit{The Interesting Data and Methods Sessions}. Series of sessions
        organised with Rachel Franklin, Elizabeth Delmelle, and Isabelle
        Nilsson at the AAG Annual Meeting. Detroit (US). April.
\item[2023] \textit{The Future of Urban Analytics}. Series of sessions
        organised between the Alan Turing Institute, the University of
        Liverpool, and the University of Leeds at the AAG Annual Meeting.
\item[2022] \textit{Workshop: Urban Analytics in Policymaking}. OECD
        Laboratory for Geospatial Analysis. Online.
\item[2021-2023] \textit{Spatial Analytics and Data - The Interviews}. Sponsored
      by the Royal Geographical Society and The Alan Turing Institute. With
        Rachel Franklin and Levi Wolf.
\item[2018] \textit{The Potential of Satellite Imagery for Studying Human
    Activity}, workshop held at the University of Liverpool. Co-organised with
    Francisco Rowe. June.
\item[2017] \textit{Geographic Data Science},  special
    sessions and panel for the Annual Meeting of the AAG , held in Boston, MA. Co-organized
    with Mark Birkin, Marynia Kolak, Nick Malleson, Alex Singleton and Seth Spielman.
\item[2016] \textit{Big Data for Urban and Regional Analysis}, special
    sessions for the Annual Meeting of the AAG , held in San Francisco, CA. Co-organized
    with Emmanouil Tranos.
\item[2014/15] \textit{Big Data Lunch Seminars}, co-organized with Emmanouil
    Tranos and University of Birmingham Institute of Advanced Studies.
\item[2015] \textit{Big Data for Urban and Regional Analysis}, special
    sessions for the Annual Meeting of the AAG , held in Chicago, IL. Co-organized
    with David Folch and Emmanouil Tranos.
\item[2014] \textit{Applications of new sources of (big) data in Regional
    Science}, special sessions for the 61st NARSC Meetings, held in
    Washington, DC. Co-organized with David Folch.
\item[] \textit{Big Data Day}, co-organized with Emmanouil
    Tranos and University of Birmingham Institute of Advanced Studies.
    September.

\item[\textbf{Participation}]

%{{{1
\item[2025] Annual Meeting of the AAG, Detroit (USA); GISRUK, Bristol (UK); Living Planet Symposium,
        Vienna (Austria).
\item[2023] Annual Meeting of the AAG, Denver (USA).
\item[2021] International Seminar on Urban Form. Glasgow (UK, online).
\item[2018] Annual Meeting of the AAG, New Orleans (USA).
\item[2017] Annual Meeting of the AAG, Boston (USA); GIS Research UK, GISRUK,
    Manchester (UK).
\item[2016] Annual Meeting of the AAG, San Francisco (USA); Workshop on Big
    Data and Transport organized by the Joint Research Centre of the European
    Comission, Sevilla (Spain); Convening on Urban
    Data Science - University of Chicago, Chicago (USA).

\item[2015] NARSC Meetings, Portland (OR, USA); 
    GIS Research UK - GISRUK, Leeds (UK); Annual Meeting of the AAG, Chicago (USA).

\item[2014] Western Regional Science Association Meeting, San Diego (USA);
    Tinbergen Institute Workshop, Amsterdam (NL); Workshop on Big Data and
    Urban Informatics, University of Illinois at Chicago (USA); Department of Economics,
    University of Houston (USA), NARSC Meetings.

\item[2013] Western Regional Science Association Meeting, Santa Barbara (USA);
    NORFACE Migration Conference, London (UK);
    Tinbergen Institute Workshop, Amsterdam (NL);
    ERSA Congress, Palermo (Italy);
    Dutch-Israeli Workshop on Regional-Science, Groningen (NL);
    5th. NORFACE Migration Conference, Berlin (Germany);
    NARSC Meetings, Atlanta (USA).

\item[2012] Spatial Econometrics Association World Conference, Salvador
    (Brazil);
    ERSA Congress, Bratislava (Slovakia);
    NORFACE ``Increasing Heterogeneity in the Workforce and its Impact'',
    Nuremberg (Germany).
    
\item[2011] Eureka Seminar, VU University, Amsterdam (NL);
    ERSA Congress, Barcelona (Spain);
    NARSC Meetings, Miami (USA);
    Tinbergen Institute Complex-City Workshop, Amsterdam (NL).

\item[2010] Workshop on Urban Dynamics URBANICS, Marbella (Chile);
    ERSA Congress, Jonk\"{o}ping (Sweden);
    Workshop Urban Systems 2.0., Delft (NL);
    FOSS4G, Barcelona (Spain).

\item[2009] Spatial Econometrics Association World Conference, Barcelona (Spain);
    NARSC Meetings, San Francisco (USA).

\item[2008] RESER, Sttutgart (Germany);
    Spatial Econometrics Association World Conference, Brooklyn (USA).

%   \item[2014] Arribas-Bel, D., Bakens, J. "The Magic’s in the Recipe - Urban
%   Diversity and Popular Amenities". NARSC, Bethesda, Washington, DC (USA)
%       November.

%   \item[2014] Arribas-Bel, D., Bakens, J. "The Magic’s in the Recipe - Urban
%   Diversity and Popular Amenities". Workshop on Big Data and
%   Urban Informatics, University of Illinois at Chicago (USA)
%       Chicago (USA). August.

%   \item[2014] Arribas-Bel, D., Bakens, J. "The Magic’s in the Recipe - Urban
%   Diversity and Popular Amenities". Department of Economics internal
%   seminars. University of Houston.
%       Houston (USA). August.

%   \item[2014] Arribas-Bel, D., Bakens, J. "Urban diversity and popular
%   amenities". Tinbergen Institute Workshop.
%       Amsterdam (Netherlands). May.

%   \item[2014] Leeuwen, E. v., Arribas-Bel, D. "Urban-rural interactions in
%       Europe: a spatial assessment at different levels". WRSA Meetings.
%       San Diego (US). February.

%   \item[2013] Arribas-Bel, D., Sanz-Gracia, F.  "On
%       the existence of agglomeration shadows at the metropolitan level".
%       NARSC Meetings. Atlanta, GA (USA). November.

%   \item[2013] Arribas-Bel, D., Florax, R. "Heterogeneity
%       and Dependence in Geo-Referenced Micro Data: Random Effects vs True
%       Contagion".
%       NARSC Meetings. Atlanta, GA (USA). November.

%   \item[2013] Arribas-Bel, D., Nijkamp, P., Poot, J. "How diverse can
%       measuring cultural diversity be? Results from agent-based simulations ".
%       NARSC Meetings. Atlanta, GA (USA). November.

%   \item[2013] Arribas-Bel, D., Nijkamp, P., Poot, J. "How diverse can
%       measuring cultural diversity be? Results from agent-based simulations ".
%       5th. NORFACE Migration Conference.
%       Berlin (Germany). November.

%   \item[2013] Arribas-Bel, D., Tranos, E., Nijkamp, P. "Thirty years of global
%       political interactions
%       A network-based look at GDELT". Dutch-Israeli Workshop on Regional Science.
%       Groningen (Netherlands). October.

%   \item[2013] Leeuwen, E. v., Arribas-Bel, D. "Urban-rural interactions in
%       Europe: a spatial assessment at different levels". 53rd ERSA Congress.
%       Palermo (Italy). August.

%   \item[2013] Arribas-Bel, D., Bakens, J. "Cultural Diversity and Popular Urban
%       Amenities" 53rd ERSA Congress.
%       Palermo (Italy). August.

%   \item[2013] Arribas-Bel, D., Sanz-Gracia "On the existence of agglomeration
%       shadows at the metropolitan level" 15th. Tinbergen Institute Workshop.
%       Amsterdam (Netherlands). May 27th-28th.

%   \item[2013] Arribas-Bel, D. "Spatial Dynamics of Cultural Diversity in the
%       Netherlands" Norface Migration conference. London (UK). April 10th-13th.

%   \item[2013] Leeuwen, E. v., Arribas-Bel, D. "Urban-rural interactions in
%       Europe: a spatial assessment at different levels" Western Regional Science Association Meeting. Santa Barbara, CA
%       (United States). February 25th-27th.

%   \item[2013] Arribas-Bel, D.; Gerritse, M. "Friends pay off: social network and
%       wages" Western Regional Science Association Meeting. Santa Barbara, CA
%       (United States). February 25th-27th.

%   \item[2012] Arribas-Bel, D.; Kourtit, K.; Nijkamp, P. "Socio-economic
%       diversity and urban buzz" Increasing Heterogeneity in the Workforce and
%       its Impact. NORFACE sponsored conference. Nurmberg (Germany). December 5th-7th.

%   \item[2012] Arribas-Bel, D. "Accidental, Big and Open: Emerging Data Sources
%       for the Understanding of Cities" Urban Futures special session, European
%       Regional Science Association (ERSA) Congress.
%       Bratislava (Slovakia). August 21th-25th.

%   \item[2012] Arribas-Bel, D.; Sanz-Gracia, F. "On the existence of
%       agglomeration shadows at the metropolitan level" European Regional Science
%       Association (ERSA) Congress.
%       Bratislava (Slovakia). August 21th-25th.

%   \item[2012] Arribas-Bel, D.; Sanz-Gracia, F. "On the existence of
%       agglomeration shadows at the metropolitan level" Spatial Econometrics
%       Association World Conference.
%       Salvador (Brazil). July 12th-13th.

%   \item[2011] Arribas-Bel, D.; Sanz-Gracia, F.; Ramos, A. "The Size Distribution
%       of Urban Employment Centers in the U.S. Metropolitan Areas" Complex-City
%       workshop, Vrije Universiteit / Tinbergen Institute.
%       Amsterdam (Netherlands). December 5th-6th.

%   \item[2011] Arribas-Bel, D.; Sanz-Gracia, F.; Ramos, A. "The Size Distribution
%       of Urban Employment Centers in the U.S. Metropolitan Areas" North American
%       Regional Science Council Annual Conference.
%       Miami (USA). November 9th-12th.

%   \item[2011] Arribas-Bel, D.; Sanz-Gracia, F.; Ramos, A. "The Size Distribution
%       of Urban Employment Centers in the U.S. Metropolitan Areas" European
%       Regional Science Association Annual Meeting.
%       Barcelona (Spain). Aug. 30th- Sept. 3rd.

%   \item[2011] Arribas-Bel, D. "GeoDaSpace: advanced spatial econometrics made
%       easy" Eureka Lunch Seminar, Dpt. of Spatial Economics, Vrije Universiteit
%       (Netherlands). Aug. 24th.

%   \item[2010] GeoDa Center for Geospatial Analysis and Computation "Python
%       Spatial Analysis Library" (Poster session).
%       FOSS4G Barcelona (Spain). September 6th-9th.

%   \item[2010] Arribas-Bel, D.; Sanz Gracia, F. "The Validity of the Monocentric
%       City Model in a Polycentric Age: US Metropolitan areas in 1990 and 2000"
%       Workshop Urban Systems 2.0. Delft (Netherlands). September 16th-17th.

%   \item[2010] Arribas-Bel, D.; Nijkamp, P; Scholten, H. "Multidimensional urban
%       sprawl in Europe: a self-organizing map approach" European Regional
%       Science Association Annual Meeting.
%       Jonk\"{o}ping (Sweden). August 23rd-25th.

%   \item[2010] Arribas-Bel, D.; Sanz Gracia, F. "\textit{How many?} Using ESDA to evaluate
%       polycentricity in the US cities" Workshop on Urban Dynamics URBANICS.
%       Marbella (Chile). March 22nd-25th.

%   \item[2009] Rey, S.J.; Anselin, L.; Folch, D. C.; Arribas-Bel,
%       D.; Sastre Gutierrez, M. L.; Interlante, L. "Measuring Spatial Dynamics of Metropolitan Areas"
%       North American Regional Science Meetings.
%       San Francisco (USA). November.
%       
%   \item[2009] Arribas-Bel, D. "\textit{How many?} Using ESDA to evaluate
%       polycentricity in the US cities" Spatial Econometrics Association.
%       Barcelona (Spain). July.

%   \item[2008] Arribas-Bel, D. ``Kangaroos, Cities and Space: the Australian Urban
%       System.''
%    Spatial Econometrics Association. Brooklyn (NY). November.

%    \item[2008] Arribas-Bel, D.; G\'{o}mez-Loscos, A.; P\'{e}rez-Xim\'{e}nez, D.
%        and Sanz-Gracia, F. "Location Patterns of Public Services Employment in
%        US Counties"
%        RESER. Stuttgart (Germany). September.

  \end{cvlist}
%}}}1
%}}}1
%}}}1
%\begin{cvlist}{Professional Associations}
%{{{1
%\item American Economics Association\\ American Statistical
% Association\\ Association of American Geographers\\ Regional Science
% Association International\\ Southern Regional Science Association\\
% Western Regional Science Association \end{cvlist}
%}}}1

\begin{cvlist}{Teaching}

\item[\textbf{Postgraduate}]

    \item Geographic Data Science (2015-2020).
        \url{https://darribas.org/gds_course}
    \item Web Mapping and Analysis (2020-). \url{https://darribas.org/wmn}
    \item Spatial Modelling for Data Scientists (2021).
        \url{https://gdsl-ul.github.io/san}
    \item Data Science Studio (2018-).
        \url{https://darribas.org/data_science_studio}
    \item Spatial Analysis (2015-20).
        \url{https://darribas.org/spa_notes}

\item[\textbf{Undergraduate}]
    \item Geographic Data Science (2015-). \url{https://darribas.org/gds_course}
    \item Virtual Field Class (2021-).
    \item Field Class Year 3, Barcelona (2015-20).
    \item Geography undergraduate dissertation supervisions (2014-2020).
    \item Field Class Year 1, Shropshire (2014).
    \item Geography Year 1 and 2 Tutorials (2014-2020).
    \item Research Methods for Dissertations (2014).


%   \item[] Coordination of Year 2 course ``GGM201-Research Methods for
%       Dissertations''.
%   \item[] Contributed lectures to courses on, Economic Geography (Year 1, three
%       sessions), Quantitative Geography
%       (Year 2, one) and New sources of (big) data in Geography (Year 3, one).

%{{{1
\item[\textbf{Workshops and Short Courses}]
\item[2026] ``Embeddings for the rest of us''.
        SPACERAISE summer school, Grand Sasso Science Institute.
        L'Aquila (Italy).
\item[2023] ``Geographic Data Science for Applied Economists'' (remote).
        15h course. CEMFI. Madrid (Spain). November.
\item[] ``Urban Analytics'' (remote). 4h session at the MSc Engineers for Smart
        Cities. Universit\'{e} C\^ote D'Azur. November.
\item[] ``Spatial autocorrelation''. Spatial Data Science Bootcamp (with
        Levi Wolf). CARTO. London. February.
\item[2022] ``Super-Charging your (Regression) Model with Space and
        Geography''. Together with Pedro Amaral. Center for Spatial Data
        Science. University of Chicago. May.
\item[2021] ``Python for Geographic Data Science''. Urban Systems Lab. Imperial
    College London. 2-day course.
    \item[] ``Geographic Data Science for Regional Economists'' (remote).
        8h course. Universitat de Val\`{e}ncia. Valencia (Spain).
    \item[] ``Geographic Data Science for Applied Economists'' (remote).
        15h course. CEMFI. Madrid (Spain).
    \item[2020] ``Enriching your Analytics with Geographic Data Science'' (remote). 2h
        workshop. Spatial Data Science Conference (online). CARTO.
    \item[] ``Geographic Data Science for Regional Scientists'' (remote). 2h
            workshop. Spanish Association of Regional Science (online) Conference.
    \item[] ``Data Science studio in Python'' (remote). 8h
        workshop. CDRC. UK.
    \item[] ``Data Science studio in Python'' (remote). 8h
        workshop. Universitat de Barcelona. Barcelona (Spain).
    \item[2019] ``Introduction to machine learning in Python''. One-day
        workshop. OECD. Paris (France).
    \item[] ``R \& Py Spatial Analysis workshop''. One-day workshop,
        jointly taught with Roger Bivand. European Colloquium on Theoretical
        and Quantitative Geography. Luxemourg.
    \item[2018] ``Geographic Data Science in Python''.
        Three-day course. University of Toronto
        (Toronto). November.
    \item[] ``Geographic Data Science in Python''.
        Three-day course. University of Luxembourg
        (Luxembourg). September.
    \item[] ``Introduction to Python for Data Science''.
        Two-day course. OECD
        (Paris). September.
    \item[] ``Python for Geographic Data Science''.
        Two-day course for the Q-Step Programme. University College London
        (UK). June.
    \item[] ``Introduction to Python for Geographic Data Science''.
        One-day course for the Consumer Data Research Centre. University of
        Leeds (UK). May.
    \item[2017] ``Geographic Data Science for Urban Analytics''.
        4 day workshop jointly taught with Alex Singleton at the Ritsumeikan
        University. Kyoto (Japan). January.
    \item[2016] ``Geographic Data Science with PySAL and the pydata stack''.
        4h workshop jointly taught with Sergio J. Rey at the 15th. annual
        Scientific Computing with Python Conference. Austin (USA). July.
    \item[2014] ``Spatial Data, Analysis and Regression mini-course''. 14h workshop taught
        at the Institute for Employment Research (IAB). Nuremberg (Germany).
        September.
    \item[] ``Workshop on open Workflows II''. 1.5 day workshop jointly taught
        with Thomas de Graaff at the Department of Spatial Economics, VU
        University. Amsterdam (Netherlands). September.
    \item[] ``Spatial Data, Analysis and Regression mini-course''. 12h workshop taught
        at the Department of Economics, University of Houston. Houston (USA).
        August.
    \item[2013] ``Geo-computation in Python''
        Workshop taught at the VII Jornadas de SIG Libre. March 6th.
        SIGTE, Universitat de Girona (Spain).
        March.
    \item[2012] ``Modeling Spatial Systems: Networks and Spatial Econometrics''
        One day intensive course jointly taught with Dr. Emmanouil Tranos.
        Department of Spatial Economics, VU University. Amsterdam (Netherlands).
        December.
    \item[] Spatial Econometrics Association World Conference. ``An
        introduction to spatial analysis and spatial econometrics with OpenGeoDa
        and GeoDaSpace''
        Salvador (Brazil). July.
    \item[] Spatial Econometrics Advanced Institute. OpenGeoDa, GeoDaSpace and
        PySAL Lab instructor.
        Catholic University. Rome (Italy). May.
     % \item Open Source Geocomputation
    \item[2009] Workshop on "Spatial Data Analysis in Ecology and Conservation",
        hosted by the National Centre for Biological Sciences in collaboration
        with the Nature Conservation Foundation and the GeoDa Center. Bangalore
        (India). July.

\item[\textbf{Assistantship}]
    \item[2010] Microeconomics II. Bachelor in Business Administration,
        Department of Economic Analysis, Universidad de Zaragoza (Spain).
        Principal instructor: Gemma Larramona. September-December.
    \item[2010] ``Mejorando la experiencia de aprendizaje de los estudiantes
        de microeconom\'{i}a intermedia. Elaboraci\'{o}n de cuestionarios de
        autoevaluaci\'{o}n en Moodle con feedback autom\'{a}tico'' (Project
        ``Improving the learning experience of intermediate microeconomics
        students. Fabrication of self-evaluation questionaires in Moodle
        with automatic feedback''). PIIDUZ-10-2-492.
        Universidad de Zaragoza. Member. 01/09/2010-30/06/2011.
        Coordinator: Domingo P\'{e}rez Xim\'{e}nez de Emb\'{u}n.


 
\end{cvlist}
%\end{cvlist}
%}}}1
\begin{cvlist}{Line management - Supervision}
%{{{1

%\item[\textbf{Department}]
%\item[2005] Chair, Computing Commitee\\
  	    %Hiring Committee

%\item[\textbf{College}]
%\item[2004] Member, Tenure and Promotion Committee

%\item[\textbf{University}]
%\item[2005] Member, Tenure and Promotion Committee, Library


%\item[\textbf{Community}]
%{{{2
%\item[1998] Technical Advisory Panel. Series 9 Demographic and
%  Economic Forecasts. San Diego Association of Governments.

%}}}2
%\item[\textbf{Profession}]
% \item[2005] Scientific Committee. Workshop on Spatial Econometrics. Kiel
%   Institute for World Economics.

\item[\textbf{Postdoctoral Researchers}]
\item[2025-] Martina Pardy. PDRA, Imago Data Service for Imagery.
\item[2025-] Fang Chen. PDRA, Imago Data Service for Imagery.
\item[2025-] Shaonlee Patranabis. PDRA, Imago Data Service for Imagery.
\item[2023-25] Stuart Lynn. Lead Research Data Scientist.
\item[2023-25] Barbara Metzler. PDRA.
\item[2020-24] Martin Fleischmann. PDRA.
\item[2022-23] Anna Zanchetta. PDRA.
\item[2021-22] Alessia Calafiore. PDRA.

\item[\textbf{PhD}]
\item{\underline{Supervisor} (\** Primary)}
\item[2025-] Baromasak Klanreungsang\**. University of Liverpool.
\item[2024-] Yuta Sato. ESRC NWSSDTP.
\item[2020-2025] Gladys Kenyon\**. ESRC CDAS CDT, with Idealista.
\item[2020-24] Qihao Liu. University of Liverpool.
\item[2019-25] James Murphy\**. ESRC CDAS CDT, with Marlan Maritime Technologies.
\item[2018-24] Danial Owen\**. ESRC CDAS CDT.
\item[2018-23] Sian Teesdale. ESRC CDAS CDT, with ESRI-Here. Unfinnished.
\item[2022] John Freeman\**. ESRC CDAS CDT, with Health \& Safety Executive. Unfinnished.
\item[2022] Meruyert Kenzhebay. ESRC CDAS CDT, with MGISS. Unfinnished.
\item[2017-22] Melanie Green\**. ESRC CDAS CDT, with Ordnance Survey.
        Unfinnished.
\item[2017-23] Krasen Samardzhiev\**. ESRC CDAS CDT, with CARTO.
\item[2018-22] Yassir Alharbi. University of Liverpool.
\item[2017-21] Nikos Patias. ESRC CDAS CDT, with Ordnance Survey.
\item[2017-21] Sam Comber\**. ESRC NWSSDTP, with Local Data Company.
\item[2016-21] Meixu Chen\**. University of Liverpool.
\item[2016-21] Yunzhe Liu. University of Liverpool.
\item[2016-21] Ellen Talbot. ESRC NWSSDTP.
\item[2016-18] Muhammad Hakim Bin Danial. University of Liverpool.
\item[2016-18] Kush Tackar. University of Liverpool.


\item{\underline{Visitor Host}}

\item[2024-25] Paula Falcao. Universidade Federal de Minas Gerais. Brazil.
\item[2023-24] Ugur Ursavas. Zonguldak B\"ulent Ecevit University. Turkey.
\item[2022] Marianna Magagnoli. Universitat de Barcelona. Spain.
\item[2019] J\'{u}lio Cesar Lopes. Universidade Cat\'olica de Bras\'ilia.
    Brazil.
\item[2017] Cassiano Ricardo Dalberto. Universidade Federal de Minas Gerais.
    Brazil.


\item{\underline{Committee Member}}
\item[2025] Job Rosier. \textit{Characterization of urban land use and urban
        land dynamics in data scarce regions}. VU University (Amsterdam).
        External examiner. April.
\item[2021] Mohammed Ibrahim. \textit{A Computer Vision System for Detecting
    and Analysing Critical Events in Cities}. University College London.
    External examiner. April.
\item[    ] Sarah Catherine Gadd. \textit{Analysing spatio-temporal networks
    with continuous-time models}. University of Leeds. External examiner.
    April.
\item[2020] Michele Ferretti. \textit{Geographies of Code: Decompiling the
    'Smart City' through the study of software engineering practices}. Kings
    College London (UK). External examiner. December.
\item[] Jacob Macdonald. \textit{Leveraging Geospatial Statistics for
    Measuring and Valuing the Urban Environment}. Universidade Nova de Lisboa
    (Portugal). Committee member. July.
\item[] Helena Nilsson. \textit{Spatial Organisation of Retail
    Activities}. J{\"o}nk{\"o}ping University. Examiner. May.
\item[2019] Alec Edward Davies. \textit{The era of repurposed data: Exploring health via Data
    Science and new forms of data}. University of Liverpool. Internal
    examiner. January.
\item[2018] Helen V. Roberts. \textit{Investigating the role of social media
        and smart device applications in understanding human-environment
    relationships in urban green spaces}. University of Birmingham. External
    examiner. February.
\item[2016] Linda Woods. \textit{A Statistical and Geographical Analysis
    of Workplace Accidents in Great Britain}. University of Liverpool.
    Internal examiner. December.
\item[2015] Jorge Eduardo Pati\~{n}o Quinch\'{i}a. \textit{Citiscape, Poverty
    and Crime: a Quantitative Assessment Using VHR Imagery}. Universitat
    Polit\`{e}cnica de Val\`{e}ncia. External referee and committee member. December.
\item[\textbf{Master}]
    %{{{2
    \item[2012]  Hada Melissa S\'{a}enz Vela. \textit{``An\'{a}lisis exploratorio de
        Caracter\'{i}sticas Socioecon\'{o}micas de M\'{e}xico mediante la
        aplicaci\'{o}n de m\'{e}todos de agregaci\'{o}n espacial, 2010''}.
        Universidad Aut\'{o}noma de Cohauila, Centro de Investigaciones
        Socioecon\'{o}micas. Lector (member of Committee). September.

\end{cvlist}
\begin{cvlist}{Service to University and Community}

\item[\textbf{Journal Referee}]
    %{{{2
    \item[]
  \emph{African Journal of Agricultural Research} (1),
  \emph{Annals of the American Association of Geographers} (1),
  \emph{Annals of GIS} (1),
  \emph{Annals of Regional Science} (4),
  \emph{Applied Geography} (3),
  \emph{Applied Spatial Analysis and Policy} (1),
  \emph{Computers, Environment and Urban Systems} (12),
  \emph{Environment and Planning A} (2) / B (12) / C (1),
  \emph{European Planning Studies} (1),
  \emph{European Urban and Regional Studies} (1),
  \emph{Geographical Analysis} (8),
  \emph{Innovation} (1),
  \emph{International Journal of Sustainable Development} (1),
  \emph{International Journal of GIS} (2),
  \emph{International Regional Science Review} (6),
  \emph{Journal of Geographical Systems} (1),
  \emph{Journal of Geography and Regional Planning} (1),
  \emph{Journal of Housing and the Built Environment} (1),
  \emph{Journal of Regional Science} (1),
  \emph{Journal of Statistical Software} (2),
  \emph{Journal of Transport Geography} (2),
  \emph{Journal of Urban Management} (1),
  \emph{Journal of Urbanism} (1),
  \emph{Landscape and Urban Planning} (1),
  \emph{Nature Human Behaviour} (1),
  \emph{Papers in Regional Science} (5),
  \emph{Proceedings of the Python in Science Conference} (2),
  \emph{REGION} (1),
  \emph{Regional Science Policy and Practice} (1),
  \emph{Regional Studies} (4),
  \emph{Spatial Economic Analysis} (4),
  \emph{Spatial Networks} (1),
  \emph{Tourism Economics} (1),
  \emph{Transactions in GIS} (3),
  \emph{Urban Geography} (2).
  \emph{Urban Studies} (3).

  % Last updated: 2018-09-18

     %}}}2
\item[\textbf{External Examination Experience}]

\item[2024-] University College London (UK): MSc in Social and Geographic Data
        Science
\item[2022-2025] University of Leeds (UK): MSc in Urban Data Science and Analytics
\item[2019-2023] University of Glasgow (UK): MSc in Urban Analytics

\item[\textbf{External Review/Panel Experience}]

\item[2021] UKRI. \textit{Agile Research and Innovation response to COVID-19 issues
    (EPSRC Panel)}. Panel member.
\item[2019] Wellcome. \textit{Open Research Fund Awards}. Panel member.
\item[2018] Jisc Geographic Data Service. \textit{Test \& Feedback Panel}. Member.

\item[\textbf{Other}]

\item[2023-] Co-host, The GLaD Podcast. \url{https://gladpodcast.podbean.com}
\item[2024] Scientific Committee Member, World Multidisciplinary Congress on
        Civil Engineering, Architecture, and Urban Planning. Ostrava (Czech
        Republic).
\item[2018] Mentor, Google Summer of Code. Project: ``\texttt{splot}:
    visualisation in PySAL''.
\item[2017] Mentor, Google Summer of Code. Project: ``Regionalization in PySAL''.
\item[2016] Mentor, Google Summer of Code. Project: ``Spatial Interaction
    Modeling in PySAL''.
\item[] Paper reviewer of the proceedings, 2016 Python for Scientific Computing
    (SciPy) Conference.
\item[2015] Paper reviewer of the proceedings, 2015 Python for Scientific Computing
    (SciPy) Conference.
\item[2014-] Young Scholars Committee Member. Centre for Geocomputation. Ryerson
    University (Canada).
\item[] Paper reviewer of the proceedings, 2014 Python for Scientific Computing
    (SciPy) Conference.
\item[] Program committee member, 2014 Python for Scientific Computing
    (SciPy) Conference.
    %{{{2
 \item[2013]  \emph{Epainos Award / Young Regional Scientist Sessions}. Reviewer.
     53rd. ERSA Congress.
     %}}}2
  \end{cvlist}

\begin{cvlist}{Scientific software}
%{{{1
\item[\underline{PySAL}] Python library of spatial analysis. Core development
    team. \url{https://pysal.org}
\item[\underline{\texttt{gds\_env}}] A containerised platform for Geographic
    Data Science. Creator and maintainer. \url{https://darribas.org/gds_env/}
\item[\underline{\texttt{contextily}}] Contextual tiles in Python. Creator and core developer. \url{https://contextily.readthedocs.io/}
\item[\underline{\texttt{xyzservices}}] XYZ basemaps in Python. Creator and developer. \url{https://xyzservices.readthedocs.io/}
\item[\underline{GeoDaSpace}] Advanced spatial econometrics. Core development
    team. 
%\item[2005-06] \emph{Regional Socieconomic Modeling in Support of Economc
%  Development Networks.} Co-Principal Investigtor.\\ Sponsor: Defense Logistics
%  Agency (\$1,200,000).

  \end{cvlist}
%}}}1
%   \begin{cvlist}{Course Attendance}
%     %{{{1
%     \item[2011] \emph{Spatial Complexity} (attendant). Special lecture series
%         taught by Michael J. Batty.
%         Arizona State University, September-October.
%     \item[] \emph{ERSA Summer School: Modelling cities and urban dynamics} (attendant),
%         University of Luxembourg, July.
%     \item[2010] \emph{Advanced Urban Modeling} (attendant),
%         Arizona State University, April-May 2010, GCU 598 (28167) and PUP 598
%         (28168), taught by Michael Batty. April-May.
%     \item[2009] \emph{European integration and networks} (attendant),
%         Master's level course in the
%         Department of Spatial Analysis of the Vrije Universiteit, taught by
%         Peter Nijkamp. September-December.
%     \item[] \emph{Geographical Information Analysis} (attendant),
%         graduate level course in the
%         School of Geographical Sciences and Planning of Arizona State University
%         (ASU), taught by Serge Rey. January-May.
%     \item[2008] \emph{Spatial Regression Analysis} (attendant), graduate level course in the
%         School of Geographical Sciences and Planning of ASU, taught by Luc
%         Anselin. August-December.
%     \item[] \emph{Spatial Econometrics Advanced Institute}, Organized by the Spatial
%       Econometrics Association at the University of La Sapienza in Rome (Italy).
%       June.
%   \item[2007] \emph{El an\'{a}lisis de las econom\'{i}as regionales} (The
%       analysis of regional economies), co-held by the International University
%       Men\'{e}ndez Pelayo and "FUNDEAR" (Foundation the economy in Arag\'{o}n), in
%       Formigal (Spain). September.
%   \item[] \emph{International Summer School}, held by the University
%       of Seoul, in
%       Seoul (Korea). July-August.
%   \item[] \emph{Cities and Economic Geography}, taught by Diego Puga
%       within the Barcelona Macroeconomics Summer School'07 at Universitat Pompeu
%       Fabra in Barcelona (Spain). June.
%   % \item[2008] Director, Regional Analysis Laboratory (REGAL), Department of
%   %   Geography, San Diego State University
%     \end{cvlist}
 
  %}}}1
\begin{cvlist}{Language Skills}
%{{{1
\item[\underline{Spanish}] Native.
\item[\underline{English}] Fluent writing, reading and speaking. Maximum level
    by the Institute of Modern Languages at the University of Zaragoza.
\item[\underline{French}] Medium writing, reading and speaking. Fourth year
    (out of five) at the Institute of Modern Languages at the University of
    Zaragoza.
  \end{cvlist}
%}}}1

\end{cv}
\end{document}
\endinput 

